---
title: "Eyetracking_lecture3"
author: "Sofia F. M. Schmidt-Kallesøe"
date: "6/2/2018"
output: html_document
---

```{r}

setwd("~/Documents/Aarhus/4. Semester/Eye tracking/Data")

library(data.table)
library(readr)
library(dplyr)
library(caret)
library(Metrics)
library(lme4)
library(lmerTest)
library(modelr)

```



```{r}

#Loading data and binding data
fixations1 = fread("FixationsV1.csv")
saccades1 = fread("SaccadesV1.csv")
samples1 = fread("SamplesV1.csv")
log1 = fread("logfile_1_2_f.csv")
log2 = fread("logfile_2_1_f.csv")
log3 = fread("logfile_3_2_f.csv")
log4 = fread("logfile_4_1_F.csv")
log5 = fread("logfile_5_2_m.csv")
log6 = fread("logfile_6_1_m.csv")
logs = rbind(log1, log2, log3, log4, log5, log6)

#Making V1 numeric so it starts counting from 1
logs$V1 = as.factor(logs$V1)
logs$V1 = as.numeric(logs$V1)

#Renaming V1 to trials
logs = rename(logs, "Trial" = "V1")
logs = rename(logs, "ParticipantID" = "subject")

#Adding variables: gender, ostensiveness, direction
logs$actorgender = substr(logs$video, start = 1, stop = 1)
logs$direction = substr(logs$video, start = 9, stop = 11)
logs$ostensiveness = substr(logs$video, start = 13, stop = 14)

#Merging logfiles with files of fixations, saccades and samples
mergedfix = merge(fixations1, logs, by = c("ParticipantID", "Trial"), all = T)
mergedsac = merge(saccades1, logs, by = c("ParticipantID", "Trial"), all = T)
mergedsam = merge(samples1, logs, by = c("ParticipantID", "Trial"), all = T)

#Making condition columns and assigning conditions to search task (search order 1 = 1-5 star search, 6-10 counting & search order 2 = 1-5 counting, 6-10 star search)
mergedfix$condition = NA
mergedsac$condition = NA
mergedsam$condition = NA

mergedfix$condition[which(mergedfix$SearchOrder == "1" & mergedfix$Trial < 6)] = "Star"
mergedfix$condition[which(mergedfix$SearchOrder == "1" & mergedfix$Trial > 5)] = "Count"
mergedfix$condition[which(mergedfix$SearchOrder == "2" & mergedfix$Trial < 6)] = "Count"
mergedfix$condition[which(mergedfix$SearchOrder == "2" & mergedfix$Trial > 5)] = "Star"

mergedsac$condition[which(mergedsac$SearchOrder == "1" & mergedsac$Trial < 6)] = "Star"
mergedsac$condition[which(mergedsac$SearchOrder == "1" & mergedsac$Trial > 5)] = "Count"
mergedsac$condition[which(mergedsac$SearchOrder == "2" & mergedsac$Trial < 6)] = "Count"
mergedsac$condition[which(mergedsac$SearchOrder == "2" & mergedsac$Trial > 5)] = "Star"

mergedsam$condition[which(mergedsam$SearchOrder == "1" & mergedsam$Trial < 6)] = "Star"
mergedsam$condition[which(mergedsam$SearchOrder == "1" & mergedsam$Trial > 5)] = "Count"
mergedsam$condition[which(mergedsam$SearchOrder == "2" & mergedsam$Trial < 6)] = "Count"
mergedsam$condition[which(mergedsam$SearchOrder == "2" & mergedsam$Trial > 5)] = "Star"

```

Complicated model for predicting fixation duration
FDuration (duration of fixations) ~ SearchType*SearchOrder*Fixations*Trial+(1+SearchType*Fixations*Trial|ParticipantID)

There are two search orders (star first - count second, count first - star second), however, the order of pictures in each search order is the same. Therefore we don't expect any systematic change for search type (star or count), however, with type for each search type there may be a systematic change (e.g. longer fixations with each search type because of boredom). Therefore, we make an interaction between searchtype and trial. However, within each trial there also may be a systematic change (e.g. longer fixations with each trial because of boredom), therefore, we make an interaction between trial and fixations. 

More simple model
FDuration ~ SearchType*Trial+(1+SearchType*Trial|ParticipantID)


```{r}

#Subsetting data to only include visual search task data
visualsearchdata = subset(mergedfix, Task == "VisualSearch")

#Participant as character first to make the system "forget" that there used to be 12 factors (across all tasks), then as factor and creating folds_id variable to give participants numbers instead of strings -
visualsearchdata$ParticipantID = as.character(visualsearchdata$ParticipantID)
visualsearchdata$ParticipantID = as.factor(visualsearchdata$ParticipantID)
visualsearchdata$folds_id = as.numeric(visualsearchdata$ParticipantID)

#Cross-validation
folds = createFolds(unique(visualsearchdata$ParticipantID), k = 3)

test_rmse = NULL
train_rmse = NULL
n = 1

#Creating loop
for(i in folds){
  #subsetting testdata
  testsubset = subset(visualsearchdata, folds_id %in% i)
  
  #subsetting traindata
  trainsubset = subset(visualsearchdata,!(folds_id %in% i))
  
  #training the model on the traindata subset
  trainmodel = lmer(Duration ~ 1 + condition + Trial + (1 + condition + Trial | ParticipantID), REML = FALSE, trainsubset)
  
  #predcting values for the dependent variable from the testdata using the training model
  pred = predict(trainmodel, testsubset, allow.new.levels = T)
  #Finding root mean squared error of the difference between the measured child MLU in the test data and the predicted child MLU
  test_rmse[n] = Metrics::rmse(testsubset$Duration, pred)
  #Finding root mean squared error of the difference between the measured child MLU in the train data and the fitted MLU values of the training model 
  train_rmse[n] = Metrics::rmse(trainsubset$Duration, fitted(trainmodel))
  
  n=n+1
}

mean(test_rmse)
mean(train_rmse)
  

```

#Social engagement task

Pupulsize ~ OST + DIR 

Should we look at pupil size during fixations or saccades?
  No processing during saccades - used be investigated during fixations
Should we look at fixation dataset (pupil size averaged over individual fixations) or sample dataset (pupil size per ms)?
  If we look at samples, we have a more finegrained grasp 
  
Pupilsize ~ OST*DIR + ACTGender*PARTGender + Trial + TrialTime + (1+TrialTime+OST+DIR|ParticipantID)
  Interaction between gender of actor and participant because the pupil size of the participant may depend on the gender of the actor depending on their gender themselves
  Ostensiveness and direction may influence each other - 


Pupilsize ~ DIR*OST*(TT+TT^2+TT^3)+ACTGEnder*PARTGEnder*(TT+TT^2+TT^3) + Trial
Interaction between gender and change the growth curve over time 
Taking into account that it might not be linear - including quadratic and cubic 



```{r}




```





